Bird beak's elaboration and innovation

### 2023-04-04 Analysis/09-Figure_key.Rmd
Update 09-Figure_key.Rmd

## Do the projection
matrix <- as.matrix(shapespace[which(shapespace$level1 == "Paleognathae"), c(1,2)])
rownames(matrix) <- NULL
## Get the base vectors
covars <- sample.n(space_paleo$covar, 1000)
centres <- lapply(unlist(space_paleo$subsets, recursive = FALSE) ,function(group, data, fun) fun(data[c(group), ]), data = space_paleo$matrix[[1]], fun = colMeans)
covars <- mapply(recentre, covars, centres, MoreArgs = list(dimensions = c(1,2)), SIMPLIFY = FALSE)
covars <- lapply(covars, function(one_covar, scale) mapply(scale.VCV, one_covar, scale, SIMPLIFY = FALSE), scale = covars[[2]])
covars_cent_tend <- lapply(covars, VCV.cent.tend, mean)
base_vectors <- lapply(lapply(covars_cent_tend, get.one.axis, axis = 1, level = 0.95, dimensions = c(1,2)), list)

@@

base <- base_vectors$Paleognathae[[1]]
base <- matrix(c(base)[c(1, 1, 4, 4)], 2, 2, byrow = FALSE) # or c(1, 4, 3, 2)
for(i in 1:nrow(matrix)) {
      lines(get.proj.line(matrix[i, ], test))
}

@@

## Transform them into a colour gradient
col.grad <- colorRamp(rev(c("#d53e4f", "#f46d43", "#fdae61", "#fee08b", "#e6f598", "#abdda4", "#66c2a5", "#3288bd")))
cols_elab <- col.grad(elaborations/max(elaborations))
cols_innov <- col.grad(innovations/max(innovations))

## Plot the tree
pdf("../Manuscript/Figures/figure_key_tree_example.pdf")
plot(tree_paleo, show.tip.label = FALSE, type = "fan")
tiplabels("", frame = "none", pch = 19, cex = 2, col = rgb(cols_elab, maxColorValue = 256), offset = -1)
tiplabels("", frame = "none", pch = 19, cex = 2, col = rgb(cols_innov, maxColorValue = 256), offset = 4)
dev.off()

>>>>

## Do the projection
matrix <- as.matrix(shapespace[which(shapespace$level1 == "Paleognathae"), c(1,2)])
rownames(matrix) <- NULL
## Get the base vectors
covars <- sample.n(space_paleo$covar, 4000)
centres <- lapply(unlist(space_paleo$subsets, recursive = FALSE) ,function(group, data, fun) fun(data[c(group), ]), data = space_paleo$matrix[[1]], fun = colMeans)
covars <- mapply(recentre, covars, centres, MoreArgs = list(dimensions = c(1,2)), SIMPLIFY = FALSE)
covars <- lapply(covars, function(one_covar, scale) mapply(scale.VCV, one_covar, scale, SIMPLIFY = FALSE), scale = covars[[2]])
covars_cent_tend <- lapply(covars, VCV.cent.tend, mean)
base_vectors <- lapply(lapply(covars_cent_tend, get.one.axis, axis = 1, level = 0.95, dimensions = c(1,2)), list)

@@

base <- base_vectors$Paleognathae[[1]]
# base <- matrix(c(base)[c(1, 1, 4, 4)], 2, 2, byrow = FALSE) # or c(1, 4, 3, 2)
for(i in 1:nrow(matrix)) {
      lines(get.proj.line(matrix[i, ], base))
}

@@

## Transform them into a colour gradient
## Change colours to grey -> blue innov. grey -> orange elab
col.grad.inno <- colorRamp(c("grey", "blue"))
col.grad.elab <- colorRamp(c("grey", "orange"))
# col.grad <- colorRamp(rev(c("#d53e4f", "#f46d43", "#fdae61", "#fee08b", "#e6f598", "#abdda4", "#66c2a5", "#3288bd")))
cols_elab <- col.grad.elab (elaborations/max(elaborations))
cols_inno <- col.grad.inno(innovations/max(innovations))

## Plot the tree
pdf("../Manuscript/Figures/figure_key_tree_example.pdf")
plot(tree_paleo, show.tip.label = FALSE, type = "fan")
tiplabels("", frame = "none", pch = 19, cex = 2, col = rgb(cols_elab, maxColorValue = 256), offset = -1)
tiplabels("", frame = "none", pch = 19, cex = 2, col = rgb(cols_inno, maxColorValue = 256), offset = 4)
dev.off()

pdf("../Manuscript/Figures/figure_key_tree_example2.pdf")
plot(ladderize(tree_paleo), show.tip.label = FALSE)
dev.off()
